Behavior Driven Development in Haskell

### 2012-05-25 paper.tex
adding open problem sections and moving cabal to BCP section.
add the "free!" paper and nub.

We agree that type signatures are good abstract document

\begin{quote}
    \emph{Should we quote "Theorems for free!" by P. Wadler here?}
\end{quote}

but there are many
functions whose behaviors cannot be guessed from their names and type
signatures.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related work}

@@

>>>>

We agree that type signatures are good abstract document~\cite{free}
but there are many
functions whose behaviors cannot be guessed from their names and type
signatures. A good example is \verb|nub :: [a] -> [a]| in 
the Data.List module.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Open problems and related work}

@@

\bibitem[Wadler 1989]{free}
Wadler P.,
``Theorems for free!'',
In proceeding of 4th International Conference on Functional Programming and Computer Architecture, 1989.
